---
title: "How To Use CGMissingDataR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How To Use CGMissingDataR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# CGMissingDataR

CGMissingDataR is an R package wrapping the CGMissingData Python library for evaluating model performance under feature missingness by: 

* injecting missing values into feature columns at specified masking rates, 
* imputing missing values using a Multiple Imputation by Chained Equations (MICE)-style iterative imputer, and
* training Random Forest and k-Nearest Neighbors regressors to report Mean ABsolute Percentage Error (MAPE) and R across missingness levels. 

## Installation

Before the installation, ensure that you have Python and the required Python packages installed. You can use the `reticulate` package to manage Python environments from R.

```r
install.packages("reticulate")
```
Install the development version of CGMissingDataR from GitHub:

``` r
devtools::install_github("saraswatsh/CGMissingDataR")
```

## Example

Below is a brief example illustrating the usage of CGMissingDataR.

```{r, setup, cache = TRUE}
library(CGMissingDataR)

# Load example dataset
tmp <- tempfile(fileext = ".csv") # Creating a temporary file to store the dataset
write.csv(CGMExampleData, tmp, row.names = FALSE) # Writing the example dataset to the temporary file
results <- run_missingness_benchmark(tmp, mask_rates = c(0.05, 0.10, 0.15, 0.20)) # Running the missingness benchmark
print(results) # Displaying the first few rows of the results
```
